Phenotype selection

### 2021-09-27 analysis/phenotype_selection.Rmd
add phenotype and couple selection schematic links
edit phenotype selection based on removing dietary traits and left-side etc

tar_load(data_phesant_directory)
tar_load(Neale_SGG_dir_filt)
tar_load(traits_corr)
tar_load(traits_corr2)
tar_load(traits_corr3)
tar_load(traits_corr4)
tar_load(traits_corr5)

@@

@@

# Non-binary.

Phenotypes were limited to `continuous_irnt` or `ordinal` (i.e. `binary` traits were removed).

@@

```{r continuous_filter, echo=FALSE}

@@

>>>>

tar_load(data_phesant_directory)
tar_load(Neale_SGG_dir_filt)
tar_load(traits_corr)
tar_load(traits_corr2)
tar_load(traits_corr3)
tar_load(traits_corr4)
tar_load(traits_corr5)
tar_load(traits_corr6)

@@

An overview of phenotype selection and exclusions can be seen [here](assets/phenotype_selection.png).

@@

# Non-diet.

Dietary phenotypes were removed due to high correlation amongst phenotypes, insufficient power and difficult interpretation.

@@

The traits remaining after removing dietary traits can be seen below.

```{r non_diet_filter, echo=FALSE}

@@

# Non-redundant phenotypes.

Lastly, left-side body traits (highly correlated with right-side) were removed and all 'qualifications' data (corresponding to field [6138](https://biobank.ctsu.ox.ac.uk/showcase/field.cgi?id=6138)) because data is roughly captured with continuous variables (such as years of education).

Number remaining after filter = **`r dim(traits_corr6)[1]`**.

The traits remaining after removing dietary traits can be seen below.

```{r non_redundant_filter, echo=FALSE}

traits_corr6.DT <- traits_corr6 %>% as_tibble() %>% mutate(r = sqrt(as.numeric(r2))) %>% dplyr::select(Neale_pheno_ID, description, variable_type, category, N_pairs, r2, r, num_IVs, num_IVs_pass_het)
DT::datatable(traits_corr6.DT, width = "100%") %>% formatRound(columns=c('r2', 'r'), digits = 3)
